### 2023-02-26 manuscript.tex
Update README with new dates [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/6ddc6c567be38982e38bb2090b00fb76430b0776.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/6ddc6c567be38982e38bb2090b00fb76430b0776/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4276965432

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/040e70b2b68ac8822e659081c5404a1ed8afe972/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/040e70b2b68ac8822e659081c5404a1ed8afe972}{SORTEE-Github-Hackathon/manuscript@040e70b}
on February 26, 2023.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/6ddc6c567be38982e38bb2090b00fb76430b0776/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/6ddc6c567be38982e38bb2090b00fb76430b0776}{SORTEE-Github-Hackathon/manuscript@6ddc6c5}
on February 26, 2023.
